\TITLE

### 2020-12-19 vonLaszewski-covid.tex
make pdflatex compile

\usepackage{calc}
\usepackage{comment}

@@

\usepackage[table]{xcolor}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating, multirow}
\usepackage{colortbl}

@@

@@

\end{description}

@@

\begin{table}[!h]
  \begin{tabular}{ll}
    \toprule
    Abbreviation & Description \\
    \midrule
    API & Application Programming Interfaces \\
    BRFSS & Behavioral Risk Factor Surveillance System \\
    CDC & Center for Desease Control \\
    CI & Cyber Infrastructure \\
    CIF21 & Cyberinfrastructure Framework for 21st Century  \\
    CINES & CyberInfrastructure for Network Engineering and Science \\
    COVID-19 & COrona VIrus Disease 2019  \\
    CSSE & Center for Systems Science and Engineering \\
    cum & cumulative \\
    DIBBS & Data Infrastructure Building Blocks \\
    FIPS & Federal Information Processing Standards \\
    GPU & Graphics Processing Unit  \\
    HPC & High Performance Computing \\
    LSTM & Long Short-Term Memory \\
    MSE & Mean Squared Error \\
    NBDIF & NIST Big Data Working Group \\
    NCHS & CDC National Center for Health Statistics \\
    NIST & National Institute of Standards and Technology \\
    NONE & \todo{NO FACTORS} \\
    NORM\_POP & Normalized Population \\
    NSF & National Science Foundation \\
    RELU & REctified Linear Unit \\
    REST & REpresentational State Transfer  \\
    RNN & Recurrent Neural Network \\
    SEIR & Susceptible, Expose, Infectious, Recovered) \\
    SELU & Scaled Exponential Linear Unit \\
    SIR &  Susceptible, Infectious, Recovered \\
    U.S. & United States of America \\
    WHO & World Health Organization \\
    \midrule
\end{tabular}
\end{table}

>>>>

\usepackage{calc}
\usepackage{comment}
\usepackage{todonotes}

@@

%\usepackage[table]{xcolor}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating, multirow}
\usepackage{colortbl}

@@

\newtheorem{requirement}{Requirement}
\newtheorem{question}{Question}

@@

@@

\begin{table}[!h]
  \begin{tabular}{ll}
    \toprule
    Abbreviation & Description \\
    \midrule
    API & Application Programming Interfaces \\
    BRFSS & Behavioral Risk Factor Surveillance System \\
    CDC & Center for Desease Control \\
    CI & Cyber Infrastructure \\
    CIF21 & Cyberinfrastructure Framework for 21st Century  \\
    CINES & CyberInfrastructure for Network Engineering and Science \\
    COVID-19 & COrona VIrus Disease 2019  \\
    CSSE & Center for Systems Science and Engineering \\
    cum & cumulative \\
    DIBBS & Data Infrastructure Building Blocks \\
    FIPS & Federal Information Processing Standards \\
    GPU & Graphics Processing Unit  \\
    HPC & High Performance Computing \\
    LSTM & Long Short-Term Memory \\
    MSE & Mean Squared Error \\
    NBDIF & NIST Big Data Working Group \\
    NCHS & CDC National Center for Health Statistics \\
    NIST & National Institute of Standards and Technology \\
    NONE & No risk factors used \\
    NORM\_POP & Normalized Population \\
    NSF & National Science Foundation \\
    RELU & REctified Linear Unit \\
    REST & REpresentational State Transfer  \\
    RNN & Recurrent Neural Network \\
    SEIR & Susceptible, Expose, Infectious, Recovered) \\
    SELU & Scaled Exponential Linear Unit \\
    SIR &  Susceptible, Infectious, Recovered \\
    U.S. & United States of America \\
    WHO & World Health Organization \\
    \midrule
\end{tabular}
\end{table}
